### 2016-07-29 main.tex
Misc. changes.  Interim checkin.

The network is trained using MATLAB's neural network toolbox. We tried
a variety of feedforward neural network geometries, from simple
1-layer perceptrons to geometries with many hidden nodes, as well as
autoencoders. Perhaps surprisingly, even the former yields excellent
results on many syllables, but a 2-layer perceptron with a very small
hidden layer---with a unit count 2-4 times the number of target
syllables---was a good compromise between accuracy and training
speed. For more variable songs, deep structure-preserving networks may
be more appropriate, but they are slow to train and unnecessary for
zebra finch song.

We used the Levenberg-Marquardt algorithm, which is the MATLAB
toolbox's default.  It is a fast algorithm, but is memory-intensive,
so many target syllables or high FFT frame rates require a large
amount of RAM and increase training time to hours. Other training
algorithms that use less RAM are much slower, and by default they will
often terminate prematurely due to their performance gradient going to
0.

@@

We divided the data into training and test sets.  For the results
reported in the following section, the training set consisted of 1000
instances of the song of one bird.
Our test set consisted of an additional 1818 iterations of the bird's
song.

The MATLAB neural network toolbox further divides our ``training'' set
into internal training, validation, and test sets.  We did not stray
from the toolbox's default values, and do not discuss MATLAB's
internal subdivision of our training set.  Because the dataset
consists of temporally aligned songs, ground truth is available for
each song (albeit with minor variations due to the alignment process
used \cite{Poole2012}), and thus the detector can be checked by
presenting the recorded training songs as well as the canonical
detection events. To this end, besides the trained network object, our
learning code produces an audio file consisting of all of the training
data on the left audio channel and a delta function at each aligned
moment of target syllable presentation on the right channel. Thus,
when played on any audio player, the left channel may be provided as
input to the detector, and the the detector's output pulses may be
compared against the right channel.

@@

We have used this detector for song alignment and feedback experiments
in 5 behaving birds, and for offline analysis on various others.  For
simplicity we present performance on 6 randomly chosen points in one
bird's song, but the results presented here are representative of
real-world performance in our lab.\marginpar{Ok?}

>>>>

The network is trained using MATLAB's neural network toolbox, with Scaled Conjugate Gradient ({\tt trainscg}). We tried
a variety of feedforward neural network geometries, from simple
1-layer perceptrons to geometries with many hidden nodes, as well as
autoencoders. Perhaps surprisingly, even the former yields excellent
results on many syllables, but a 2-layer perceptron with a very small
hidden layer---with a unit count 2-4 times the number of target
syllables---was a good compromise between accuracy and training
speed. For more variable songs, deep structure-preserving networks may
be more appropriate, but they are slow to train and unnecessary for
zebra finch song.

@@

We divided the data into training and test sets.  For the results
reported in the following section, the training set consisted of 1000
instances of the song of one bird, and 2000 song-length samples of
non-song (cage noise, calls, other birds' song).  Our test set
consisted of an additional 1818 iterations of the bird's song and 3636
song-length samples of non-song.

The MATLAB neural network toolbox further divides our ``training'' set
into internal training, validation, and test sets.  Because we do our
own testing on a distinct and much larger data set, we instructed the
toolbox to use 80\% of its training set for training, and the
remaining 20\% for validation, with no hold-out test data.

Because the data set consists of temporally aligned songs, ground
truth is available for each song (albeit with minor variations due to
the alignment process used \cite{Poole2012}), and thus the detector
can be checked by presenting the recorded training songs as well as
the canonical detection events. To this end, besides the trained
network object, our learning code produces an audio file consisting of
all of the training data on the left audio channel and a delta
function at each aligned moment of target syllable presentation on the
right channel. Thus, when played on any audio player, the left channel
may be provided as input to the detector, and the the detector's
output pulses may be compared against the right channel.

@@

We have used this detector for song alignment and feedback experiments
in 5 behaving birds, and for offline analysis on a few others.  For
simplicity we present performance on 6 randomly chosen points in one
bird's song, but the results presented here are representative of
real-world performance in our lab.\marginpar{Ok?}
